 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-04-22 paper.Rmd
update case study section

@@

@@

>>>>

?? include details of tour here

@@

In this case study we explore some simulated noisy tree structured data (figure \@ref(fig:fake-trees)), our interest here is how t-SNE visualisations break topology of the data, and then seeing if we can resolve this by tweaking the default parameters
with reference to the global view of the data set.

@@

First, we apply principal components and restrict the results down to the first twelve principal components (which makes up approximately 70% of the variance explained in the data) to use with the grand tour.

<!-- can we show R code? -->

Moreover,
we run t-SNE using the default arguments on the complete data (this keeps the first 50 PCs, sets the perpelxity to equal 30 and performs random initalisation) using the `Rtsne` package [@Rtsne]. We then create a linked tour with t-SNE layout with `liminal` as shown in the following video :

<embededded video 1>

From the video, we see that the t-SNE view has been unable to recapitulate the topology of the tree - the backbone (blue) branch has been split into two fragments. We can see this immediately via the linked highlighting over both plots. If we click on the legend for the zeroth branch, the blue colored points on each view are higlighted and the remaining points are made transparent. From, here it becomes apparent from the tour view that the blue branch forms the backbone of the tree and is connected to all other branches.
